---
title: "gapminder-analysis"
author: "Anna Krystalli"
date: "5/1/2018"
output: 
  html_document:
      toc: true
      toc_float: true
      theme: cosmo
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```




Excerpt from the [Gapminder](http://www.gapminder.org/data/) data. The main object in this package is the `gapminder` data frame or "tibble". 


# Installation

Install `gapminder` from CRAN:

```{r, eval=FALSE}
install.packages("gapminder")

```

Or you can install `gapminder` from GitHub:

```{r, eval=FALSE}
devtools::install_github("jennybc/gapminder")
```



## DATA


```{r}
gapminder_df <- readr::read_csv(here::here("data", "raw", "gapminder.csv"))
```

```{r}
DT::datatable(gapminder_df, caption = "gapminder dataset sourced from the gapminder r package")
```

### Visual summary of the data

```{r}
library(skimr)
skim(gapminder_df)
```


## Relationship between GDP per capita and Life Expectancy

```{r, echo=FALSE}
library(ggplot2)

gapminder_df %>% ggplot(aes(x = gdpPercap, y = lifeExp)) +
    geom_point()
```

### Linear model of Life expectancy as a function of GDP per capita

```{r}
library(broom) # great for extracting model parameter summaries
lm(lifeExp ~ gdpPercap, data = gapminder_df) %>% broom::glance()
```




```{r, echo=TRUE}
library(ggplot2)

gapminder_df %>% ggplot(aes(x = gdpPercap, y = lifeExp, color = continent)) +
    geom_point() + scale_x_log10() 
```

### Linear model of Life expectancy as a function of GDP per capita

```{r}
library(broom) # great for extracting model parameter summaries
lm(lifeExp ~ log10(gdpPercap), data = gapminder_df) %>% broom::glance()
```



```{r, message=FALSE}
meta_tbl <- readr::read_csv(here::here("data", "metadata", "gapminder_meta.csv"))
```

### Add smooth lines

```{r, echo=TRUE}
library(ggplot2)

gapminder_df %>% ggplot(aes(x = gdpPercap, y = lifeExp, color = continent)) +
    geom_point() + scale_x_log10() + geom_smooth()
```
